---
title: "Statistical Analysis: Comparing NARA Scores between Young Adults and Older Adults"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
```

# Introduction

This analysis compares NARA scores between Young Adults (YA) and Older Adults (OA) to determine if there are statistically significant differences between the groups. We will systematically test assumptions and select the most appropriate statistical test.

# Load Required Libraries

```{r libraries}
# Load required libraries
library(tidyverse)
library(car)        # for Levene's test
library(nortest)    # for additional normality tests
library(ggplot2)
library(gridExtra)  # for arranging plots
library(knitr)      # for nice tables
library(kableExtra) # for enhanced tables
library(diptest)
```

# Data Import and Initial Exploration

```{r data-import}
# Read your data
data <- read.csv("/Volumes/YB_Drive/NavAging_Paper/data/non_nav_data.csv")

# Check data structure
str(data)
```

```{r data-summary}
# Basic summary
summary(data)
```

## Group and NARA Variable Overview

```{r group-nara-overview}
# Look at Group and NARA variables specifically
cat("Group variable summary:\n")
table(data$Group)

cat("\nNARA variable summary:\n")
summary(data$NARA)

# Check for missing values
missing_summary <- data.frame(
  Variable = c("Group", "NARA"),
  Missing_Count = c(sum(is.na(data$Group)), sum(is.na(data$NARA))),
  Missing_Percent = c(
    round(sum(is.na(data$Group))/nrow(data)*8, 2),
    round(sum(is.na(data$NARA))/nrow(data)*8, 2)
  )
)

kable(missing_summary, caption = "Missing Data Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r data-cleaning}
# Remove rows with missing NARA or Group data
data_clean <- data[!is.na(data$NARA) & !is.na(data$Group), ]
cat("Original dataset size:", nrow(data), "participants\n")
cat("Clean dataset size:", nrow(data_clean), "participants\n")
cat("Rows removed:", nrow(data) - nrow(data_clean), "\n")
```

# Descriptive Statistics

```{r descriptive-stats}
# Calculate descriptive statistics by group
desc_stats <- data_clean %>%
  group_by(Group) %>%
  summarise(
    n = n(),
    mean = round(mean(NARA, na.rm = TRUE), 3),
    sd = round(sd(NARA, na.rm = TRUE), 3),
    median = round(median(NARA, na.rm = TRUE), 3),
    q1 = round(quantile(NARA, 0.25, na.rm = TRUE), 3),
    q3 = round(quantile(NARA, 0.75, na.rm = TRUE), 3),
    min = round(min(NARA, na.rm = TRUE), 3),
    max = round(max(NARA, na.rm = TRUE), 3),
    .groups = 'drop'
  )

kable(desc_stats, caption = "Descriptive Statistics by Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Data Visualization

## Distribution Plots

```{r distribution-plots, fig.height=8}
# Create histograms for each group
p1 <- ggplot(data_clean, aes(x = NARA, fill = Group)) +
  geom_histogram(alpha = 0.7, bins = 15, position = "identity") +
  facet_wrap(~Group) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Distribution of NARA Scores by Group",
       x = "NARA Score", y = "Frequency") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

# Create boxplot
p2 <- ggplot(data_clean, aes(x = Group, y = NARA, fill = Group)) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.5) +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "NARA Scores by Group",
       x = "Group", y = "NARA Score") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

# Arrange plots
grid.arrange(p1, p2, ncol = 1)
```

## Normality Assessment: Q-Q Plots

```{r qq-plots}
# Q-Q plots for normality assessment
ggplot(data_clean, aes(sample = NARA)) +
  geom_qq() +
  geom_qq_line(color = "red") +
  facet_wrap(~Group) +
  theme_minimal() +
  labs(title = "Q-Q Plots for Normality Assessment",
       subtitle = "Points should follow the red line if data is normally distributed") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))
```

# Assumption Testing

## Normality Tests

```{r normality-tests}
# Test for Normality (by group)
groups <- unique(data_clean$Group)
normality_results <- data.frame()

for(group in groups) {
  group_data <- data_clean[data_clean$Group == group, "NARA"]
  shapiro_result <- shapiro.test(group_data)
  
  normality_results <- rbind(normality_results, data.frame(
    Group = group,
    n = length(group_data),
    W_statistic = round(shapiro_result$statistic, 4),
    p_value = round(shapiro_result$p.value, 4),
    Normal = ifelse(shapiro_result$p.value >= 0.05, "Yes", "No")
  ))
}

kable(normality_results, caption = "Shapiro-Wilk Normality Tests by Group") %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_footnote("Normal = Yes if p ≥ 0.05 (fail to reject normality)")
```

```{r normality-interpretation}
# Overall normality assessment
all_normal <- all(normality_results$Normal == "Yes")
cat("Overall normality assumption met:", all_normal, "\n")
```

## Homogeneity of Variance Test

```{r variance-test}
# Levene's test for homogeneity of variance
levene_result <- leveneTest(NARA ~ Group, data = data_clean)

variance_summary <- data.frame(
  Test = "Levene's Test",
  F_statistic = round(levene_result$`F value`[1], 4),
  df1 = levene_result$Df[1],
  df2 = levene_result$Df[2],
  p_value = round(levene_result$`Pr(>F)`[1], 4),
  Equal_Variances = ifelse(levene_result$`Pr(>F)`[1] >= 0.05, "Yes", "No")
)

kable(variance_summary, caption = "Homogeneity of Variance Test") %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_footnote("Equal_Variances = Yes if p ≥ 0.05")

equal_var <- variance_summary$Equal_Variances == "Yes"
cat("Equal variances assumption met:", equal_var, "\n")
```

## Sample Size Assessment

```{r sample-size}
# Sample size check
group_sizes <- table(data_clean$Group)
sample_size_summary <- data.frame(
  Group = names(group_sizes),
  n = as.numeric(group_sizes),
  Adequate_Size = ifelse(as.numeric(group_sizes) >= 30, "Yes (≥30)", "Small (<30)")
)

kable(sample_size_summary, caption = "Sample Size Assessment") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

min_size <- min(group_sizes)
cat("Minimum group size:", min_size, "\n")
```

# Test Selection Decision

```{r test-decision}
# Create decision summary
decision_summary <- data.frame(
  Assumption = c("Normality", "Equal Variances", "Adequate Sample Size"),
  Met = c(all_normal, equal_var, min_size >= 30),
  Details = c(
    paste("All groups normal:", all_normal),
    paste("Equal variances:", equal_var),
    paste("Min n =", min_size)
  )
)

kable(decision_summary, caption = "Assumption Testing Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Determine recommended test
if(all_normal && equal_var) {
  recommended_test <- "Independent samples t-test (equal variances)"
  test_type <- "parametric"
} else if(all_normal && !equal_var) {
  recommended_test <- "Welch's t-test (unequal variances)"
  test_type <- "parametric"
} else {
  recommended_test <- "Mann-Whitney U test (non-parametric)"
  test_type <- "non-parametric"
}
```

## **Recommended Test: `r recommended_test`**

**Rationale:** 
- Normality assumption: `r ifelse(all_normal, "✓ Met", "✗ Violated")`
- Equal variances assumption: `r ifelse(equal_var, "✓ Met", "✗ Violated")`
- Sample size: `r ifelse(min_size >= 30, "✓ Adequate", "⚠ Small")`

# Statistical Test Results

## Parametric Tests

```{r parametric-tests}
if(length(groups) == 2) {
  # Standard t-test (assuming equal variances)
  t_test_equal <- t.test(NARA ~ Group, data = data_clean, var.equal = TRUE)
  
  # Welch's t-test (not assuming equal variances)
  t_test_welch <- t.test(NARA ~ Group, data = data_clean, var.equal = FALSE)
  
  # Create results table
  parametric_results <- data.frame(
    Test = c("Independent t-test (equal var)", "Welch's t-test (unequal var)"),
    t_statistic = c(round(t_test_equal$statistic, 4), round(t_test_welch$statistic, 4)),
    df = c(round(t_test_equal$parameter, 2), round(t_test_welch$parameter, 2)),
    p_value = c(round(t_test_equal$p.value, 4), round(t_test_welch$p.value, 4)),
    CI_lower = c(round(t_test_equal$conf.int[1], 3), round(t_test_welch$conf.int[1], 3)),
    CI_upper = c(round(t_test_equal$conf.int[2], 3), round(t_test_welch$conf.int[2], 3))
  )
  
  kable(parametric_results, caption = "Parametric Test Results") %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    add_footnote("CI = 95% Confidence Interval for difference in means")
  
  # Effect size (Cohen's d)
  group1_data <- data_clean[data_clean$Group == groups[1], "NARA"]
  group2_data <- data_clean[data_clean$Group == groups[2], "NARA"]
  
  pooled_sd <- sqrt(((length(group1_data)-1)*var(group1_data) + 
                     (length(group2_data)-1)*var(group2_data)) / 
                    (length(group1_data) + length(group2_data) - 2))
  
  cohens_d <- (mean(group1_data) - mean(group2_data)) / pooled_sd
  
  if(abs(cohens_d) < 0.2) {
    effect_interpretation <- "negligible"
  } else if(abs(cohens_d) < 0.5) {
    effect_interpretation <- "small"
  } else if(abs(cohens_d) < 0.8) {
    effect_interpretation <- "medium"
  } else {
    effect_interpretation <- "large"
  }
  
  effect_size_summary <- data.frame(
    Measure = "Cohen's d",
    Value = round(cohens_d, 3),
    Interpretation = effect_interpretation
  )
  
  kable(effect_size_summary, caption = "Effect Size") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

## Non-Parametric Test with Effect Size

```{r nonparametric-test-enhanced}
# Mann-Whitney U test
mann_whitney <- wilcox.test(NARA ~ Group, data = data_clean)

# Calculate rank biserial correlation (effect size for Mann-Whitney U test)
group1_data <- data_clean[data_clean$Group == groups[1], "NARA"]
group2_data <- data_clean[data_clean$Group == groups[2], "NARA"]

n1 <- length(group1_data)
n2 <- length(group2_data)
U <- mann_whitney$statistic

# Calculate rank biserial correlation
# Method 1: Using U statistic
r_rb <- 1 - (2 * U) / (n1 * n2)

# Alternative method: Using mean ranks
combined_data <- c(group1_data, group2_data)
combined_ranks <- rank(combined_data)
group1_ranks <- combined_ranks[1:n1]
group2_ranks <- combined_ranks[(n1+1):(n1+n2)]

mean_rank1 <- mean(group1_ranks)
mean_rank2 <- mean(group2_ranks)

# Alternative calculation method
r_rb_alt <- (mean_rank1 - mean_rank2) / ((n1 + n2) / 2)

# Effect size interpretation
if(abs(r_rb) < 0.1) {
  rb_interpretation <- "negligible"
} else if(abs(r_rb) < 0.3) {
  rb_interpretation <- "small"
} else if(abs(r_rb) < 0.5) {
  rb_interpretation <- "medium"
} else {
  rb_interpretation <- "large"
}

# Create comprehensive results table
nonparametric_results_enhanced <- data.frame(
  Test = "Mann-Whitney U",
  W_statistic = round(mann_whitney$statistic, 4),
  p_value = round(mann_whitney$p.value, 4),
  Alternative = mann_whitney$alternative,
  n_group1 = n1,
  n_group2 = n2,
  rank_biserial_r = round(r_rb, 3),
  effect_size = rb_interpretation
)

kable(nonparametric_results_enhanced, caption = "Non-Parametric Test Results with Effect Size") %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_footnote(c(
    "Rank biserial correlation ranges from -1 to 1",
    "Effect size: |r| < 0.1 = negligible, 0.1-0.3 = small, 0.3-0.5 = medium, > 0.5 = large"
  ))

# Additional details table
effect_details <- data.frame(
  Measure = c("Rank Biserial Correlation", "Mean Rank Group 1", "Mean Rank Group 2"),
  Value = c(round(r_rb, 4), round(mean_rank1, 2), round(mean_rank2, 2)),
  Interpretation = c(rb_interpretation, "", "")
)

kable(effect_details, caption = "Effect Size Details") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

# Print interpretation
cat("📊 RANK BISERIAL CORRELATION INTERPRETATION:\n")
cat("r =", round(r_rb, 3), "(", rb_interpretation, "effect)\n\n")

if(r_rb > 0) {
  cat("↗️ ", groups[1], "tends to have higher ranks than", groups[2], "\n")
} else {
  cat("↘️ ", groups[2], "tends to have higher ranks than", groups[1], "\n")
}

cat("\n📋 EFFECT SIZE GUIDELINES (Rank Biserial Correlation):\n")
cat("• |r| < 0.1  = Negligible effect\n")
cat("• |r| 0.1-0.3 = Small effect\n") 
cat("• |r| 0.3-0.5 = Medium effect\n")
cat("• |r| > 0.5   = Large effect\n")
```

## Function for Easy Calculation

```{r rank-biserial-function}
# Create a reusable function for rank biserial correlation
calculate_rank_biserial <- function(x, y) {
  # x and y are numeric vectors for the two groups
  n1 <- length(x)
  n2 <- length(y)
  
  # Perform Mann-Whitney U test
  test_result <- wilcox.test(x, y)
  U <- test_result$statistic
  
  # Calculate rank biserial correlation
  r_rb <- 1 - (2 * U) / (n1 * n2)
  
  # Effect size interpretation
  if(abs(r_rb) < 0.1) {
    interpretation <- "negligible"
  } else if(abs(r_rb) < 0.3) {
    interpretation <- "small"
  } else if(abs(r_rb) < 0.5) {
    interpretation <- "medium"
  } else {
    interpretation <- "large"
  }
  
  return(list(
    r_rb = r_rb,
    interpretation = interpretation,
    U_statistic = U,
    p_value = test_result$p.value,
    n1 = n1,
    n2 = n2
  ))
}

# Example usage of the function
result <- calculate_rank_biserial(group1_data, group2_data)
cat("Function result - Rank biserial r:", round(result$r_rb, 3), 
    "(", result$interpretation, "effect)\n")
```

# Results Summary

```{r results-summary}
# Determine significance
if(test_type == "parametric") {
  if(equal_var) {
    final_p <- t_test_equal$p.value
    final_test <- "Independent samples t-test"
  } else {
    final_p <- t_test_welch$p.value
    final_test <- "Welch's t-test"
  }
} else {
  final_p <- mann_whitney$p.value
  final_test <- "Mann-Whitney U test"
}

significance <- ifelse(final_p < 0.05, "Yes", "No")
```

## **Final Results**

**Test Used:** `r final_test`  
**p-value:** `r round(final_p, 4)`  
**Statistically Significant (α = 0.05):** `r significance`

```{r final-interpretation}
if(significance == "Yes") {
  cat("🔍 INTERPRETATION: There IS a statistically significant difference in NARA scores between groups.\n")
} else {
  cat("🔍 INTERPRETATION: There is NO statistically significant difference in NARA scores between groups.\n")
}

if(exists("cohens_d")) {
  cat("📊 EFFECT SIZE: Cohen's d =", round(cohens_d, 3), "(", effect_interpretation, "effect )\n")
}
```

# Recommendations for Reporting

```{r reporting-recommendations}
cat("REPORTING RECOMMENDATIONS:\n\n")

if(test_type == "non-parametric") {
  cat("• Report medians and interquartile ranges instead of means and standard deviations\n")
  cat("• Use Mann-Whitney U test results\n")
  cat("• Mention assumption violations that led to non-parametric approach\n")
} else {
  cat("• Report means and standard deviations\n")
  cat("• Include effect size (Cohen's d)\n")
  cat("• Report confidence intervals\n")
  if(!equal_var) {
    cat("• Note that Welch's correction was used due to unequal variances\n")
  }
}

cat("\nADDITIONAL CONSIDERATIONS:\n")
cat("• Check for outliers that might influence results\n")
cat("• Consider the practical significance of any statistical differences\n")
cat("• Verify that the groups are appropriate for comparison\n")
```

# Session Information

```{r session-info}
sessionInfo()
```